Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}

### 2021-03-13 paper/main.tex
restructuring introduction

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{IEEEkeywords}
Domotic plugs; Reliable UDP; ADD MORE
\end{IEEEkeywords}

\section{Introduction}
Nowadays, keeping track of the domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances. In most cases the solution is a sensor connected to the main safety switch yielding the total energy consumption. Our approach, to get more detailed information and to have control on the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line. In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the main server and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure. This consists of: the smart plugs, a central processing unit (for the main server) and a device (for the web interface). In a home scenario these devices are connected to the home wireless router. The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level, and tested using Wireshark \cite{wireshark}. The smart plugs have been prototyped using Arduino and the server has been written in Java. Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances. When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance. This value is then updated to reflect the real maximum power usage of the appliance. Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less then the available power. Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN. To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power on of appliances that consume more then the available power. It also gives granular information about the devices consumption and allows the user to turn on or off appliances remotely (via web interface). Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower then the real one in order to use less power or save money.

\section{General architecture}
The architecture implemented differs from the most common architectures used in this scenario in two major aspects, first most homes don't have this kind of system even in place, instead a circuit breaker triggers for safety reasons when too much power is being consumed. Second, when a similar system is used it usually relies on cloud computing or external services. In contrast our system offers the functionalities already described and both computing and data storage are done locally. This can be an advantage in terms of both privacy and security. Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN. However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section. The architecture of the system is such that if need be it can be easily modified to use third party services.

The general architecture has 3 main components: the smart plugs, an UDP server, the web interface.

>>>>

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{IEEEkeywords}
Domotic plugs; Reliable UDP;
\end{IEEEkeywords}

\section{Introduction}
Nowadays, keeping track of domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances. In most cases, the solution is a sensor connected to the main safety switch yielding the total energy consumption. Our approach, to get more detailed information and to have control over the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line. In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the server, and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consumption-driven infrastructure. This consists of the smart plugs, a computer (for the server), and a device (for the web interface). In a home scenario, these devices are connected to the home wireless router. The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}. The architecture implemented differs from the most common ones in two major aspects: first, most homes aren't equipped with this kind of system, instead, a circuit breaker triggers for safety reasons when too much power is being consumed. Second, when a similar system is used it usually relies on cloud computing or external services. In contrast, our system offers the functionalities already described and both computing and data storage are performed locally. This can be an advantage in terms of both privacy and security. Furthermore, this is an advantage in terms of reliability: our system doesn't need an internet connection to work properly, instead, it just needs a working WLAN. However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section. The architecture of the system is such that if need be it can be easily modified to use third-party services. The smart plugs have been prototyped using Arduino and the server has been written in Java. Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances. When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance. This value is then updated to reflect the real maximum power usage of the appliance. Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less than the available power. Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN. To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power-on of appliances that consume more than the available power. It also gives granular information about the energy consumption of the device and allows the user to turn on or off appliances remotely (via web interface). Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower than the real one to use less power or save money.

\section{General architecture}
The general architecture has 3 main components: the smart plugs, the server, and the web interface.
